\cvsection{Experience}
\begin{cventries}
  \cventry
    {Summer Research Assistant}
    {The University of Chicago, Department of Astronomy and Astrophysics}
    {Chicago, IL}
    {June 2015 - Aug. 2017} 
    {
      \begin{cvitems}
        \item {Measured diffuse interstellar bands (DIBs - anomalous absorption features resulting from unknown atomic and molecular carriers in space).}
        \item {Assembled program in Java for quicker note taking and analysis.}
        \item {Designed and presented poster in research symposium at Stevenson High School.}
      \end{cvitems}
    }
  \cventry
    {Founder and Full-Stack Developer}
    {SuccessHS}
    {Buffalo Grove, IL}
    {June 2017 - Present}
    {
      \begin{cvitems}
        \item {SuccessHS is a tutoring service that hopes to simplify the process of getting students in touch with tutors.}
        \item {Founded SuccessHS and developed the SuccessHS app which helps students get in touch with tutors faster and with more ease.}
        \item {Implemented Ionic and Angular for front end development, with Firebase for back end development.}
        \item {App can be found at: bit.ly/successhsandroid}
      \end{cvitems}
    }
    
    \cventry
      {Developer -- Worked on OpenCV}
      {PennApps - Hackathon}
      {University of Pennsylvania}
      {January 2018}
      {
        \begin{cvitems}
            \item Collaborated on a real time whiteboard app that would augment student tutor interaction by using the computer vision library OpenCV to allow users to write in the air by detecting the user's fingertip. Technologies include React for the front end and Python + OpenCV + Firebase for the backend.
        \end{cvitems}
    }
    
    \cventry
      {Developer}
      {15-112 Term Project}
      {Carnegie Mellon University}
      {September 2017}
      {
        \begin{cvitems}
            \item Designed "Fruit Ninja-esque" game called Candy Catcher in which players are to "catch" flying candy with their mouth. 
            \item Implemented with OpenCV and dlib for facial landmark recognition as well as mouth open/closed detection.
        \end{cvitems}
    }
    
    
    \cventry
      {Developer}
      {HackPrinceton}
      {Princeton University}
      {November 2017}
      {
        \begin{cvitems}
            \item Collaborated on building an educational quantum computing app. 
            \item Researched and summarized quantum computing ideas to build web app.
            \item Technologies include Vue.js for front end and Flask for back end.
        \end{cvitems}
    }
    
    \cventry
      {Developer}
      {HackCMU}
      {Carnegie Mellon University}
      {September 2017}
      {
        \begin{cvitems}
            \item Hacked on a receipt sorter app which takes pictures and organizes information on receipt for easy reading to user.
        \end{cvitems}
    }
    
\end{cventries}
